\documentclass[11pt]{amsbook}

\usepackage{../HBSuerDemir}	
\usepackage[utf8]{inputenc}
\usepackage{enumitem}


\begin{document}
% ++++++++++++++++++++++++++++++++++++++
\hPage{b2p1/020}
% ++++++++++++++++++++++++++++++++++++++

Theorem.
%\underline{Theorem}.

\renewcommand{\labelenumi}{\alph{enumi})}
\begin{enumerate}
\item In a convergent series, the general term tends to zero, 
\item If, in a series, the general terms does not tend to zero, the series is divergent.

\end{enumerate}

We call Part b test for divergence by general-term test.

%\vspace{4mm}

%\underline{Proof}.
Proof.
\renewcommand{\labelenumi}{\alph{enumi})}
\begin{enumerate}
\item Let $\sum_{1} a_{n} = s$. Then $a_{n} = s_{n+1} - s_{n} \rightarrow s - s = 0$
\item Let $a_{n} \rightarrow k\neq 0$, but suppose the series is convergent. 

\end{enumerate}
Then by a$)$, $a_{n} \rightarrow 0$ contradicting $k\neq 0$.

%\vspace{4mm}

%\underline{Remark}. 
Remark. As the harmonic series shows, the approach of $a_{n}$ to zero does not imply the convergence of the series, that is, the series in which $a_{n} \rightarrow 0$ may converge or diverge.
\
Test for convergence and divergence are generally given for series of positive terms.

%\vspace{4mm}
B.SERIES OF POSITIVE TERMS
%B. \underline{SERIES OF POSITIVE TERMS}

%\vspace{4mm}
A series having almost every term (all terms except perhaps finitely many ones) positive is called a series of positive terms.
%Actually, I write \underline{series of positive terms} but Haluk hoca says you ignore \underline in your hw.
\\
Thus the series 

\begin{center}
$\sum_{1}\frac{1}{n}$, $\sum_{0}\left | a_{n} \right |$, $\sum_{1}\frac{n^{2} - 2n - 3}{n^{2}} = - 4  - \frac{3}{4} - 0  + \frac{5}{6} + ... + \frac{n^{2} - 2n - 3}{n^{2}} + .$
\end{center}
are series of positive terms, while $ \sum_{0}\left ( \frac{-1}{2} \right )^{n} $ is not.

%\vspace{4mm}
The tests that are given here are comparison tests by which a given series of positive terms is compared either with a positive improper integral or with another series of positive terms. There are also intrinsic tests which are applied directly to a given series itself.



\end{document}
