%Correct the file name.
%X: book number
%Y: part number
%ZZZ: page number in three digits. So page 3 would be 003.

\documentclass[11pt]{amsbook}

\usepackage{../HBSuerDemir}	% ------------------------

\theoremstyle{definition}

\newtheorem{definition}{Definition}


\begin{document}

% ++++++++++++++++++++++++++++++++++++++
\hPage{feyzioglu-007}
% ++++++++++++++++++++++++++++++++++++++



\centerline{\textbf{ยง2}}
\centerline  {\textbf{Equivalence Relations}}

\vspace{1cm}

\noindent In mathematics, we often investigate relationships between  certain
objects (numbers, functions, sets, figures, etc.). If an element a of $a$ set$ A$
is related  to an element $b$ of a set $B$, we might write \\
\centerline  {$a$ is related to $b$ }
or shortly\\
\centerline  {$a$  related  $b$ }
or even more shortly \\
\centerline  {$a \ R \ b$ }

\noindent The essential point is that we have two objects; a and b, that are related
in some way. Also, we say "$a$ is related to $b$", not "$b$ is related to $a$",so
the \textit{order} of $a$ and $b$ is important. In other words, the ordered pair$(a ,b)$
is distinguished by the relation. This observation suggests the following
formal definition of a relation. 
\begin{definition}
	Let A and B two sets. A \textit{relation R from A into B} is a subset of the cartesian product A $\times$B.
\end{definition}
\noindent If $A$ and $B$ happen to be equal, we speak of a relation on $A$ instead of
using the longer phrase "a relation from$A$ into $A$"\\

\noindent Equivalence relations constitute a very important type of relations on a
set. 
\begin{definition}
	Let A be a nonempty set. A relation \textit{R} on A (that is, a subset \textit{R} of \textit{R$\times$R}) is called and \textit{equivalence relation on A} if the following holds:
\end{definition}
\begin{enumerate}[label=(\roman*)]
	\item $(a,a)$ $\epsilon$ $R$ for all $a$ $\epsilon$ $ A$, 
	\item if $(a,b)$ $\epsilon$ $R$, then $(b,a)$ $\epsilon$ $R$ (for all $a,b$ $\epsilon$ A). 
	\item if $(a,b)$ $\epsilon$ $R$ and $(b,c$) $\epsilon$ R, then $(a,c)$ $\epsilon$ $R$ 
\end{enumerate}
(for all $ a,b,c $ $\epsilon$ $R$)

\end{document}
