\documentclass[11pt]{amsbook}
\usepackage{../HBSuerDemir}
\begin{document}
    \hPage{b1p2/504}
    \begin{hEnumerateAlpha}
        \item to the top of the tank, 
        \item to a level k ft above the top of the tank.
    \end{hEnumerateAlpha}
    
    \begin{hEnumerateArabic}
        \setcounter{enumi}{42}
    
        \item A trough 20 ft long has a cross section in the shape of an isoceles trapezoid with a lower base 4 ft long, an upper base 10 ft long and an altitude of 4 ft. How much work is done in filling the trough with water if the bottom of the trough is located 20 ft above the pump and the water is pumped in through a valve in the bottom of the trough?
     
        \item A force of 20 kg is required to compress a spring 20 cm long to 19 cm. What is the work done in stretching the spring from a length of 24 cm to 30 cm?
        
        \item A vertical cylindrical tank 6 dm in diameter and 10 dm height is half full of water. Find the amount of work done in pumping all the water to the top of the tank.
        
        \item According to NEWTON's law of universal gravitation two objects of weights $w_{1}$, $w_{2} $ kg are attracted to each other by a force of
              $$k \frac{w_{1}w_{2}}{x^2}  kg,$$

        \noindent where x is the distance between the objects and k is a
        constant. Find the work done in separating the objects from a distance of "a meters" to a distance of "b meters" apart.
        
        \item Find the amount of work done in stretching a spring from its natural length of 8 cm to triple that length if a force of 15 kg is needed to triple it natural length.
        
        \item Find moments of the following arc with respect to x- and y- axes, and find also the centroid of the arc if $\delta$ = 1. 
    
    \end{hEnumerateArabic}

\end{document}
