\documentclass{book}
\usepackage{../HBSuerDemir}
\usepackage{caption}
\usepackage{enumitem}
\usepackage{amsmath}
\renewcommand{\figurename}{Şekil}
\captionsetup[figure]{labelsep=space}
\usepackage{fancyhdr}
\fancyhf{}
\fancyhead[L]{\thepage}
\pagestyle{fancy}
\fancypagestyle{plain}
\fancyhf{}
\fancyhead[L]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\begin{document}
\hPage{feyzioglu-020}
\begin{defn}
	Let \hFunction{f}{A}{B} be a mapping. If every element of $B$ is the second component of at most one order pair of $f$, then $f$ is called a \underline{one-to-one} mapping from $A$ to $B$.
\end{defn}
A function \hFunction{f}{A}{B} is therefore one-to-one if an arbitrary element of $B$ has either no preimage in $A$ or exactly one preimage: any two preimages of $b\in B$ (if $b$ has a preimage at all) must be equal. So the necessary and sufficient condition for a mapping: \hFunction{f}{A}{B} to be one-to-one is 
\begin{flalign*}
	&& af=b \textit{ and } a_{1}f=b \Longrightarrow a=a_{1} && (a,a_{1}\in A, b \in B)
\end{flalign*}
or, more shortly
\begin{flalign*}
	&& af=a_{1}f \Longrightarrow a=a_{1} && (a,a_{1}\in A),
\end{flalign*}
whose contrapositive reads
\begin{flalign*}
	&& a\neq a_{1} \Longrightarrow af\neq a_{1}f && (a,a_{1}\in A)
\end{flalign*}
A one-to-one mapping is a mapping by which different elements in the domain are matched with different elements in the range. Being a one-to-one function is the negation of being a "many-to-one" function, by which many elements in the domain are matched with one and the same element in the range.
	\begin{exmp}
		\begin{enumerate}[label=(\alph*)]
			\item \hPairingCurly{\hPairingParan{x,y}: x^{2}=y} $\subseteq$ \hSoR X \hSoR is not a one-to-one function from \hSoR into \hSoR, for two distinct elements $x$ and $~x$ (if $x\neq 0$) have the same image.
			\item Let \hSoRp denote the set of all positive real numbers. Then the mapping \hPairingCurly{\hPairingParan{x,y}: x^{2}=y} $\subseteq$ \hSoRp X \hSoRp is a one-to-one function from \hSoRp into \hSoRp.
			\item The mapping $g: \hPairingCurly{1,2,3} \to \hPairingCurly{a,b,c,d}$, given by 
			\begin{flalign*}
			1g=b,2g=d,3g=a,
			\end{flalign*}
			is one-to-one.
			\item Let $A$ be a nonempty set. Then $ı_{A}: A \to A$ is one-to-one, for if $aı_{A}=bı_{A}$, then $a=b$ from the definition of $ı_{A}$.
		\end{enumerate}
	\end{exmp}
\end{document}